Template for indicator documentation

### 2023-09-13 insectIndicators.Rmd
Render book with insect chapter

---
title: "Template for indicator documentation"
output:
  html_document
---

@@

@@

```{r, eval=FALSE}

@@

```{r, echo = FALSE}
poll_loc_year <- readRDS("data/cache/poll_loc_year.RDS")
poll_loc_year %>% 
  slice(1:5) %>% 
kableExtra::kbl()
```

@@

```{r, eval=FALSE}
semi_loc <- get_localities(dataset = "NasIns",
                           habitat_type = "Semi-nat")

@@

```{r, echo=FALSE}
semi_loc<-readRDS("data/cache/semi_loc.RDS")
```

@@

@@

```{r,eval=FALSE, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGrassland2022 <- getAllData(type = "bumblebees",
                                     habitat = "gressmark",
                                     year = 2022,
                                     language = "norsk")

@@

```{r, echo=FALSE}
allBombusGrassland2022<-readRDS("data/cache/allBombusGrassland2022.RDS")
```

@@

```{r, eval=FALSE}
bombus_trond_2022 <- getComplData(type = "Humler",
                                  region_short = "Trond",
                                  habitat = "Gressmark",
                                  year = 2022)
```

```{r, echo=FALSE}
bombus_trond_2022<-readRDS("data/cache/bombus_trond_2022.RDS")
```

@@

```{r, eval=FALSE}
exp_bombus_trond <- getExpValues(type = "Humler",
                                 region_short = "Trond",
                                 habitat = "Gressmark")
```

```{r}
exp_bombus_trond<-readRDS("data/cache/exp_bombus_trond.RDS")
```

@@

```{r, eval=FALSE}
getDiffWeights()

@@

```{r, echo=FALSE}
diffWeights<-readRDS("data/cache/diffWeights.RDS")
diffWeights
```

```{r, eval=FALSE}
getAmountWeights()
```

```{r, echo=FALSE}
amountWeights<-readRDS("data/cache/amountWeights.RDS")
amountWeights
```

@@

```{r, eval=FALSE}
hInd2022TrondGress <- calcInd(type = "Humler",
                              region_short = "Trond",
                              habitat = "Gressmark",
                              year = 2022,
                              nIter = nIter,
                              save.draws = T)
```

```{r, echo=FALSE}
hInd2022TrondGress<-readRDS("data/cache/hInd2022TrondGress.RDS")
```

@@

```{r}
#connect_to_insect_db()
norway_regions <- Norimon::get_map()
norway_reg_NorIns <- norway_regions %>% 
  filter(region != "Vestlandet") %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))
```

@@

```{r}
nbbm_norway_regions <- bombLepiSurv::get_map()
norway_reg_NBBM <- nbbm_norway_regions %>% 
  filter(region %in% c("Øst", "Sørlandet", "Trøndelag", "Vestlandet")) %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))
```

@@

Fetch the data.
```{r, eval=FALSE}
biomass_sn <- get_biomass(subset_year = 2020:2022,
                          subset_region = NULL)
```

```{r, echo=FALSE}
biomass_sn<-readRDS("data/cache/biomass_sn.RDS")
```

@@

Fetch the data.
```{r, eval=FALSE}
richness_sn <- get_observations(subset_year = 2020:2022,
                                subset_region = NULL)
```

```{r, echo=FALSE}
richness_sn<-readRDS("data/cache/richness_sn.RDS")
```

@@

```{r, eval=FALSE}
pollinators_sn <- get_observations(subset_year = 2020:2022,
                                   subset_families = pollinator_fam,
                                   subset_region = NULL)
```

```{r, echo=FALSE}
pollinators_sn<-readRDS("data/cache(pollinators_sn.RDS")
```

@@

Calculate the indicator values for each region and year.
```{r}
dung_sn_boot <- bootstrap_value(df = dung_sn,
                                       value = no_species,
                                       groups = c("year",
                                                  "region_name")
                                       )
```
Compare to arbitrary reference value and normalize.
```{r}
dung_ref <- 90

@@

Fetch the data.
```{r}
richness_sn <- get_observations(subset_year = 2020:2022,
                                subset_region = NULL)
```
Calculate the indicator values for each region and year.
```{r}
gde_sn_boot <- bootstrap_value(df = richness_sn,
                                   value = GDE_by_asv,
                                   groups = c("year",
                                              "region_name")
                                   )
```

@@

```{r bombusGressBarplot,eval=FALSE, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGressmark2022 <- getAllData(type = "bumblebees",
                          habitat = "gressmark",
                          year = 2022,
                          language = "norsk")

@@

```{r, echo=FALSE}
allBombusGressmark2022<-readRDS("data/cache/allBombusGressmark2022.RDS")

surveyBarplot(allBombusGressmark2022)
```

@@

@@

norway_reg_NBBM <- bombLepiSurv::get_map() %>% 
  filter(region %in% c("Sør", "Vestlandet", "Øst", "Trøndelag")) %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))

>>>>

@@

```{r, echo=FALSE}
connect_to_insect_db(user=Sys.getenv("INSECT_USER"), password=Sys.getenv("INSECT_PASSWORD"))
```

@@

@@

```{r}
poll_loc_year %>% 
  slice(1:5) %>% 
kableExtra::kbl()
```

@@

```{r}
semi_loc <- get_localities(dataset = "NasIns",
                           habitat_type = "Semi-nat")

@@

@@

```{r, echo=FALSE}
bombLepiSurv::humlesommerfConnect(username = Sys.getenv("BOMB_USER"), Sys.getenv("BOMB_PASSWORD"))
```

@@

```{r, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGrassland2022 <- getAllData(type = "bumblebees",
                                     habitat = "gressmark",
                                     year = 2022,
                                     language = "norsk")

@@

@@

```{r}
bombus_trond_2022 <- getComplData(type = "Humler",
                                  region_short = "Trond",
                                  habitat = "Gressmark",
                                  year = 2022)
```

@@

```{r}
exp_bombus_trond <- getExpValues(type = "Humler",
                                 region_short = "Trond",
                                 habitat = "Gressmark")
```

@@

```{r}
getDiffWeights()

@@

```{r}
getAmountWeights()
```

@@

```{r}
hInd2022TrondGress <- calcInd(type = "Humler",
                              region_short = "Trond",
                              habitat = "Gressmark",
                              year = 2022,
                              nIter = nIter,
                              save.draws = T)
```

@@

```{r, eval=FALSE}
connect_to_insect_db()
norway_regions <- Norimon::get_map()

```{r, echo=FALSE}
connect_to_insect_db(user=Sys.getenv("INSECT_USER"), password=Sys.getenv("INSECT_PASSWORD"))
norway_regions <- Norimon::get_map()

```{r}
norway_reg_NorIns <- norway_regions %>% 
  filter(region != "Vestlandet") %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))
```

@@

```{r}
nbbm_norway_regions <- bombLepiSurv::get_map()
```

norway_reg_NBBM <- nbbm_norway_regions %>% 
  filter(region %in% c("Øst", "Sørlandet", "Trøndelag", "Vestlandet")) %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))
```

@@

Fetch the data.
```{r}
biomass_sn <- get_biomass(subset_year = 2020:2022,
                          subset_region = NULL)
```

@@

```{r}
richness_sn <- get_observations(subset_year = 2020:2022,
                                subset_region = NULL)
```

@@

```{r}
pollinators_sn <- get_observations(subset_year = 2020:2022,
                                   subset_families = pollinator_fam,
                                   subset_region = NULL)
```

@@

Calculate the indicator values for each region and year.
```{r}
dung_sn_boot <- bootstrap_value(df = dung_sn,
                                       value = no_species,
                                       groups = c("year",
                                                  "region_name")
                                       )
```
Compare to arbitrary reference value and normalize.

```{r}
dung_ref <- 90

@@

Fetch the data.
```{r}
richness_sn <- get_observations(subset_year = 2020:2022,
                                subset_region = NULL)
```

Calculate the indicator values for each region and year.

```{r}
gde_sn_boot <- bootstrap_value(df = richness_sn,
                                   value = GDE_by_asv,
                                   groups = c("year",
                                              "region_name")
                                   )
```

@@

```{r, echo=FALSE}
require(bombLepiSurv)
humlesommerfConnect(username = Sys.getenv("BOMB_USER"), password = Sys.getenv("BOMB_PASSWORD"), host = "ninradardata01.nina.no")

@@

```{r bombusGressBarplot, fig.cap = "Bumblebees in grasslands 2021"}
allBombusGressmark2022 <- getAllData(type = "bumblebees",
                          habitat = "gressmark",
                          year = 2022,
                          language = "norsk")

surveyBarplot(allBombusGressmark2022)

@@

```{r}
norway_reg_NBBM <- bombLepiSurv::get_map() %>% 
  filter(region %in% c("Sør", "Vestlandet", "Øst", "Trøndelag")) %>% 
  select(region) %>% 
  group_by(region) %>% 
  summarize(geom = st_union(geom))

@@
